Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-06 paper.qmd
Updated Figure title

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 5
#| fig-width: 15
#| fig-pos: H
#| out-height: 50%
#| fig-cap: "The sparse end of the structure exhibits a high model error, while the dense end shows a low model error. The tSNE layouts of the C-shaped structure, with uniform points (a1) and dense points (b1) are colored according to their high-dimensional error, along with their selected projections (a2 and b2), are displayed. Darker colors represent a high error, while lighter colors indicate a low error. The uniformly distributed points demonstrate random model errors throughout the structure, whereas the dense structure shows large model error at the sparse end. Videos of the langevitour animations are available at <>."

>>>>

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 5
#| fig-width: 15
#| fig-pos: H
#| out-height: 50%
#| fig-cap: "The sparse end of the structure shows a high model error, while the dense end shows a low model error. The tSNE layout of the C-shaped structure, with dense points (a) are colored according to their high-dimensional error. Darker colors represent a high error, while lighter colors indicate a low error. b and c present the results from linked plots that highlighted the high-dimensional error points in \\gD{} and $4\\text{-}D$. Videos of the linked plots are available at <>."
